Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-05 ms.tex
rewriting bandpass correction section to reflect switch to per-MBB approach

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. In practice, 
however, we wish to constrain our model using measurements in the broad 
\IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
computed dimensionless bandpass correction factors $b_{\nu_i}$ such that 
$M_{\nu_i}b_{\nu_i}$ is the predicted observation for the \PLANCK~or \IRAS~band
 of interest, in MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the five 
nominal band center frequencies for which we have broadband measurements, 
$\nu_i \in$ \{217, 353, 545, 857, 3000\} GHz. The shape of model spectrum 
$M_{\nu}$ is only dependent upon one parameter: the hot dust temperature $T_2$.
 We have used the \PLANCK~transmission curves provided in the file 
\verb|HFI_RIMO_R1.10.fits| \citep{planckresponse}. For 3000 GHz, we have used 
the \IRAS~bandpass, following the treatment of \cite{planckdust}. We note that 
it is not clear which bandpass should properly be ascribed to the \IRAS/DIRBE 
composite 100$\mu$m maps under consideration.

>>>>

\subsection{Finite Bandpass Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
intensity $M_{\nu}$ in MJy/sr for any single frequency $\nu$. In practice, 
however, we wish to constrain our model using measurements in the broad 
\IRAS/\PLANCK~bandpasses, typically hundreds of GHz wide. We have therefore 
computed dimensionless bandpass correction factors:$b_{\nu_i}(T, \alpha)$

\begin{equation}
b_{\nu_i}(T, \alpha) = 
\end{equation}

The two-component model prediction in band $\nu_i$ is then constructed
as a linear combination of color-corrected MBB terms as:

\begin{equation}
M_{\nu_i}b_{\nu_i}
\end{equation}

%pre-computing lookup tables of b_{\nu_i} allows us to evaluate the 
% relevant modified blackbodies at the nominal  band center frequency 
% and then obtain the broadband measurement by virtue of multiplying by
% by the relevant b_{\nu_i}

Is the predicted observation for the \PLANCK~or \IRAS~band of interest, in 
MJy/sr. Here $\nu_i$ represents the $i^{th}$ of the 
five nominal band center frequencies for which we have broadband measurements, 
$\nu_i \in$ \{217, 353, 545, 857, 3000\} GHz. We have used the 
\PLANCK~transmission curves provided in the file \verb|HFI_RIMO_R1.10.fits| 
\citep{planckresponse}. For 3000 GHz, we have used the DIRBE bandpass.

% We note that it is not clear which bandpass should properly be ascribed to 
% the \IRAS/DIRBE composite 100$\mu$m maps under consideration.
